---
title: "homework3"
format: html
---

link: https://github.com/chloecarlstrom/ENVS-193DS_homework-03.git

```{r}
library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(ggplot2)


personal_data <- read.csv("data/ENVS 193DS personal data csv - data.csv", header = TRUE)


```

#Problem 1

##a. 
For comparing time spent on campus/in class to daily step count, I could compare means of both groups to see if there is a correlation between the two variables. I would also want to compare the categorical variable of "type of workout" against step count to see if a particular workout type is correlated with higher step counts. Then to combine the two concepts I would also want to look if there is any relation between type of workout and the average amount of time spent on campus, for example if I spent less time on campus and in class, am I more likely to workout and/or have a higher step count. 

##b. 

```{r}
ggplot(data = personal_data, aes(x = time_spent_on_campus, y = step_count, color = type_of_workout)) +
  geom_point(size = 3) +
  scale_color_manual(values = c(run = "royalblue", bike = "deeppink", none = "honeydew4", swim = "aquamarine", yoga = "magenta3",kayak = "orange3", hike = "forestgreen" )) +
  labs(
    title = "Daily Step Count vs Time Spent on Campus \ncolored by Type of Workout",
    x = "Time Spent on Campus (hours)",
    y = "Daily Step Count",
    color = "Type of Workout"
  ) +
  theme_minimal()

```








```

